---
title: "Data science project - Suicidial attacks"
author: "Mr.Jakob Alderson & Mr.Tal Bracha"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r, echo= FALSE, message=FALSE}
library(tidyverse)
library(mapview)
library(sf)
library(ggplot2)
library(ggmap)
library(tseries)
library(car)
library(moments)
library(writexl)
library(AID)
library(leaflet)
```


## Intro - why its importent?
The main reasons suicide attacks are particularly important to research are:
  
  *Suicide attacks are five times more lethal than ordinary attacks.
  
  *In the last 5 years suicide attacks have become more and more common, and have been used in 40% of all conflicts in comparison to 4% in the 80s.
  
  *Suicide attacks have become a popular combat tactic among militant groups, especially when combating stronger    military forces.
  
  *Due to their shocking nature they amplify militant group’s propaganda efforts.
  
  *Suicide attacks also increase recruitment by demonstrating the group's ideological commitment.

## Research question 

What is the connection between human capital and the lethality of suicidal attacks? 

## litetature 1 - Human Capital and the Productivity of Suicide Bombers

 
Benmelech's and Berrebi's article (2017) provides the first detailed empirical analysis of the relationship
between suicide bomber's characteristics and their performance in a suicide bombing
attacks, The conclusion was that Palestinian terror organizations match older and
more-educated suicide bombers to more important Israeli targets, another conclusion was that older and more-educated suicide bombers kill more people in their suicide attacks
when assigned to important targets.
Furthermore, older and more-educated suicide bombers are less likely to fail or to be caught when they
attack.

This paper also contributes to the debate on the relation between education, poverty, and terrorism. While suicide bombers are on average more
educated than the general Palestinian population, their estimate of a higher
education among suicide bombers is three times lower than the figures reported by Berrebi
(2003) and Krueger and Maleckova (2003).

## litetature 2 - What’s Special about Female Suicide Terrorism?

O'Rourke's article (2009) analyzes the interaction between the motivations of individual attackers and terrorist group strategies.
To do so it combines a quantitative analysis of all known suicide terrorist attacks between 1981 and July 2008 with a strategic account of why terrorist
organizations employ female suicide terrorism and case studies of individual female attackers.
The author advances five main claims:

1)She reveals the superior effectiveness of female suicide terrorism from the perspective of the groups that employ women.

2)She explains that terrorist groups increasingly enlist women as suicide attackers because of their higher effectiveness.

3)She demonstrates that terrorist groups adapt their discourse, catering to the specific individual motives of potential female suicide attackers to recruit them.

4)She shows that female attackers are driven by the same general motives and circumstances that drive men.

5)She concludes that, unless target states adapt their defensive strategies, we should expect an increase in female suicide terrorism.


## Suicidal attacks global or middle eastern problem?

```{r}
points = read.csv("attacks.csv")
points = points[!is.na(points$latitude), ]
points = points[!is.na(points$longitude), ]
```

```{r, warning=FALSE}

world <- map_data("world")
   ggplot() +
     geom_map(
       data = world, map = world,
       aes(long, lat, map_id = region),
       color = "black", fill = "lightgray", size = 0.1
     ) +
     geom_point(
       data = points,
       aes(longitude, latitude), color = "blue",
       alpha = 0.7
     ) 
```

Points density:
```{r}
ggplot(points, aes(x = longitude, y = latitude)) + 
     geom_point() + 
     coord_equal() + 
     xlab('longitude') + 
     ylab('latitude') + 
     stat_density2d(aes(fill = ..level..), alpha = 100,
                    geom = "polygon", data = points) + 
     scale_fill_viridis_c() + 
     theme(legend.position = 'none') 
```

The middle east  is the brightest

## Data Cleaning and Normaliry transformation:

Before cleaning:

```{r}
attacks = read.csv("attacks.csv")
head(as_tibble(attacks))
```
 
After some data cleaning:
```{r}
attacks = as_tibble(attacks) %>%
  select(event_id,wounded_low,wounded_high,killed_low,killed_high) %>%
  filter(wounded_low >= 0) %>%
  filter(wounded_high >= 0) %>%
  filter(killed_low >= 0) %>%
  filter(killed_high >= 0) %>%
  mutate(wounded_average = ceiling(((wounded_low + wounded_high)/2) )) %>%
  mutate(killed_average = ceiling(((killed_low + killed_high)/2) )) %>% 
  mutate(casualties = wounded_average + killed_average) %>%
  filter(casualties < 500) %>%
  select(event_id,wounded_average,killed_average,casualties)
 head(attacks)
```

## Normality visualtization:

```{r}
par(mfrow = c(1,3))
hist(attacks$wounded_average, breaks = length(attacks$wounded_average))
hist(attacks$killed_average, breaks = length(attacks$killed_average))
hist(attacks$casualties, breaks = length(attacks$casualties))

```

The data is in Poisson distribution, we have a massive positive right skew. 

```{r}
par(mfrow = c(1,3))
qqPlot(attacks$wounded_average, id= FALSE)
qqPlot(attacks$killed_average, id= FALSE)
qqPlot(attacks$casualties, id= FALSE)
```



## Square root data transformation:

```{r}
par(mfrow = c(1,3))
hist(sqrt(attacks$wounded_average + 1 ))
hist(sqrt(attacks$killed_average + 1 ))
hist(sqrt(attacks$casualties + 1))

```

## Log(10) data transformation: 

```{r}
par(mfrow = c(1,3))
hist(log10(attacks$wounded_average + 1 ))
hist(log10(attacks$killed_average + 1 ))
hist(log10(attacks$casualties + 1 ))

```

## Inverse data transformation:

```{r}
par(mfrow = c(1,3))
hist(1/(attacks$wounded_average + 1 ))
hist(1/(attacks$killed_average + 1 ))
hist(1/(attacks$casualties + 1))

```

## log 10 looks like normal distribution, but what’s the problem?

```{r}
agostino.test(log10(attacks$casualties+1))
```

## too many repetitions! 

```{r}
qqPlot(log10(attacks$casualties+1),id= FALSE)
```


```{r}
attacks2 = attacks %>%
  count(casualties, sort = TRUE) %>%
  filter(casualties < 30)


      ggplot(data = attacks2, aes(x=casualties, y=n)) +
  geom_bar(stat="identity", width=0.5)

```

We did our best but you cant transform poisson distribution with low lambda

## Age and Suicidal Attacks correlation and regression 

```{r}
attackers = read.csv("attackers.csv") 
head( as_tibble(attackers) )
```

 
```{r}
attackers_new = attackers %>%
  as_tibble() %>%
  select(event_id,attacker_id,age_time_death,gender,birth_admin0_txt) %>%
  filter(age_time_death > 0) 
  head(attackers_new)
```

## Male correlation  
```{r}
male_attackers = attackers_new %>%
filter(gender == "Male") %>%
inner_join(attacks, by =  "event_id") %>%
select(age_time_death,wounded_average,killed_average,casualties,gender)
head(male_attackers)

```

```{r}
res<-cor.test(male_attackers$age_time_death,male_attackers$wounded_average, method="kendall")
res$p.value
```

```{r}
res2<-cor.test(male_attackers$age_time_death,male_attackers$killed_average, method="kendall")
res2$p.value
```

```{r}
res3<-cor.test(male_attackers$age_time_death,male_attackers$casualties, method="kendall")
res3$p.value
```


## Male regression  

```{r}
res4= glm(casualties ~  age_time_death, data = male_attackers , family = "poisson"	)
summary(res4)
```

## Female correlation 

```{r}
female_attackers = attackers_new %>%
filter(gender == "Female") %>%
inner_join(attacks, by =  "event_id") %>%
select(age_time_death,wounded_average,killed_average,casualties,gender)
head(female_attackers)
```

```{r}
fes<-cor.test(female_attackers$age_time_death,female_attackers$wounded_average, method="kendall")
fes$p.value
```

```{r}
fes2<-cor.test(female_attackers$age_time_death,female_attackers$killed_average, method="kendall")
fes2$p.value
```

```{r}
fes3<-cor.test(female_attackers$age_time_death,female_attackers$casualties, method="kendall")
fes3$p.value
```

## Female regression 

```{r}
fes4= glm(killed_average ~  age_time_death, data = female_attackers , family = "poisson"	)
summary(fes4)
```

## Male vs Female - wounded average

```{r, }
both_gender1 = bind_rows(male_attackers,female_attackers) %>%
  select(gender,wounded_average )
test <- wilcox.test(both_gender1$wounded_average ~ both_gender1$gender)
test$p.value
```

```{r, message=FALSE}
ggplot(both_gender1, aes(x= wounded_average, color=gender)) +
  geom_histogram(fill="white")
```

## Male vs Female - killed average
```{r, message=FALSE}
both_gender2 = bind_rows(male_attackers,female_attackers) %>%
  select(gender,killed_average )
test2 <- wilcox.test(both_gender2$killed_average ~ both_gender2$gender)
test2$p.value
```

```{r, message=FALSE}
ggplot(both_gender2, aes(x= killed_average, color=gender)) +
  geom_histogram(fill="white")
```

## Male vs Female - Casualties


```{r}
both_gender3 = bind_rows(male_attackers,female_attackers) %>%
  select(gender,casualties )
test3 <- wilcox.test(both_gender3$casualties ~ both_gender3$gender)
test3$p.value

```

```{r, message=FALSE}
ggplot(both_gender3, aes(x= casualties, color=gender)) +
  geom_histogram(fill="white")
```

```{r}
ggplot(data = male_attackers) + 
      geom_point(mapping = aes(x = age_time_death, y = casualties)) +
      geom_smooth(mapping = aes(x = age_time_death, y = casualties)) 
      

```

## compare  other poeple 
```{r}
options(dplyr.print_max = 1e9)
attackers_new %>%
  group_by(birth_admin0_txt) %>% 
  summarise(n = n()) %>%
  arrange(desc(n))

```

```{r}
library(tidyverse)
library(leaflet)

leaflet(data = points) %>%
  addTiles() %>%
  addMarkers(lat=points$latitude, lng=points$longitude, clusterOptions = markerClusterOptions(),
             popup= paste("<strong>Date: </strong>", points$date_day,"/",points$date_month,"/", points$date_year,
                          "<br><br><strong>Place: </strong>", points$city_txt,"-",points$admin0_txt,
                          "<br><strong>Killed_low_estimate: </strong>", points$killed_low,
                          "<br><strong>Killed_high_estimate: </strong>", points$killed_high,
                          "<br><strong>wounded_low_estimate: </strong>", points$wounded_low,
                          "<br><strong>wounded_high_estimate: </strong>", points$wounded_high,
                          "<br><strong>wepon: </strong>", points$weapon_txt
                          
                          
             ))
```


