---
title: "Updated_Tal"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Data science project - Suicidial attacks"
author: "Mr.Jakob Alderson & Mr.Tal Bracha"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r, echo= FALSE, message=FALSE}
library(tidyverse)
library(mapview)
library(sf)
library(ggplot2)
library(ggmap)
library(tseries)
library(car)
library(moments)
library(writexl)
library(AID)
```


## Intro - why its importent?
The main reasons suicide attacks are particularly important to research are:
  
  *Suicide attacks are five times more lethal than ordinary attacks.
  
  *In the last 5 years suicide attacks have become more and more common, and have been used in 40% of all conflicts in comparison to 4% in the 80s.
  
  *Suicide attacks have become a popular combat tactic among militant groups, especially when combating stronger    military forces.
  
  *Due to their shocking nature they amplify militant group’s propaganda efforts.
  
  *Suicide attacks also increase recruitment by demonstrating the group's ideological commitment.



## Our research question and hypothesis 

Is there a connection between human capital and the lethality of suicidal attacks? 

According to the literature we except to see that indices like sex, age and socioeconomic status will affect the leathality of suicidal attacks.

we expect that there is a strong relationship between older age and higher unemployment rate to the leathality of suicide attacks.  In particular
woman will more leathel than men.


In addition we expect to see a raise in popularity of female suicide attacks,and we excpect women to use more consiled weapons than men like belt bomb.

## Our database

In our project we used "The Database on Suicide Attacks (DSAT)" from the university of Chicago it contains specific information for all suicide attacks committed in modern history, from 1982 to 2019. Event records in the DSAT are highly detailed and coded for over 60 variables (not including source information).

The variables are divided into five broad categories:

1.Basic information, including attack location, date, and casualty counts.

2.Target information, including target type category (security / political / civilian) and their relation to state or international infrastructure.

3.Attacker biographical information, including attacker name, age, gender, nationality, and religious affiliation.

4.Claim information, including a list of groups that explicitly claim or deny credit for an attack, as well as groups suspected of involvement.

5.Sources, including texts of news articles and wire service alerts used in coding the attack.

## Litetature 1 - Human Capital and the Productivity of Suicide Bombers

 
Benmelech's and Berrebi's article (2017) provides the first detailed empirical analysis of the relationship
between suicide bomber's characteristics and their performance in a suicide bombing
attacks, The conclusion was that Palestinian terror organizations match older and
more-educated suicide bombers to more important Israeli targets, another conclusion was that older and more-educated suicide bombers kill more people in their suicide attacks
when assigned to important targets.
Furthermore, older and more-educated suicide bombers are less likely to fail or to be caught when they
attack.

This paper also contributes to the debate on the relation between education, poverty, and terrorism. While suicide bombers are on average more
educated than the general Palestinian population, their estimate of a higher
education among suicide bombers is three times lower than the figures reported by Berrebi
(2003) and Krueger and Maleckova (2003).

## Litetature 2 - What’s Special about Female Suicide Terrorism?

O'Rourke's article (2009) analyzes the interaction between the motivations of individual attackers and terrorist group strategies.
To do so it combines a quantitative analysis of all known suicide terrorist attacks between 1981 and July 2008 with a strategic account of why terrorist
organizations employ female suicide terrorism and case studies of individual female attackers.
The author advances five main claims:

1)She reveals the superior effectiveness of female suicide terrorism from the perspective of the groups that employ women.

2)She explains that terrorist groups increasingly enlist women as suicide attackers because of their higher effectiveness.

3)She demonstrates that terrorist groups adapt their discourse, catering to the specific individual motives of potential female suicide attackers to recruit them.

4)She shows that female attackers are driven by the same general motives and circumstances that drive men.

5)She concludes that, unless target states adapt their defensive strategies, we should expect an increase in female suicide terrorism.

## Litetature 3 - Economic Conditions and the Quality of Suicide Terrorism

In this article Benmelech et al.(2010) analyze the link between economic conditions and the leathality of suicide terrorism. litreature up to that point showed that poverty and econmic conditions didnt affect the quantity of terror.
Focusing on Palestinian suicide terrorists against Israeli targets between the years
2000 and 2006 they wantd to check the correlation between economic conditions the characteristics of suicide terrorists and the targets they attack.
They concluded that poor economic conditions and high unemployment enable terror organizations recruit more educated, mature and experienced suicide terrorists who attack more important targets. 

## Litetature 4 - Wolves in Sheep’s Clothing: Assessing the Effect of Gender Norms on the Lethality of Female Suicide Terrorism

In this research Thomas(2021) shows that the gender of the attackers and the gender norms in the country they made the attack influence the leathality of the attack using data on individual suicide attacks from 1985 to 2015.
She concluded that women are more lethal than men when it comes to suicide attacks but only in countries with restrictive gender norms and practices because in those countries women seen as pacific and apolitical therefore they dont seen as a threat by the people. And in country where women seen as equal to men they didn't have a edge when it comes to the leathality of the attack.

Moreover, Terrorists have also exploited the association between motherhood and innocence by deploying expectant mothers or women pretending to be pregnant in suicide attacks, by being pregnant or faking to be pregnant women are able to conceal their weapon (like vests and belts) more effectively also some scholars suggest that pregnancy may further discourage frisks, providing female terrorists greater cover.

## Suicidal attacks global or middle eastern problem?

```{r}
points = read.csv("attacks.csv")
points = points[!is.na(points$latitude), ]
points = points[!is.na(points$longitude), ]
```

```{r, warning=FALSE}

world <- map_data("world")
   ggplot() +
     geom_map(
       data = world, map = world,
       aes(long, lat, map_id = region),
       color = "black", fill = "lightgray", size = 0.1
     ) +
     geom_point(
       data = points,
       aes(longitude, latitude), color = "blue",
       alpha = 0.7
     ) 
```

Points density:
```{r}
ggplot(points, aes(x = longitude, y = latitude)) + 
     geom_point() + 
     coord_equal() + 
     xlab('longitude') + 
     ylab('latitude') + 
     stat_density2d(aes(fill = ..level..), alpha = 100,
                    geom = "polygon", data = points) + 
     scale_fill_viridis_c() + 
     theme(legend.position = 'none') 
```

The middle east  is the brightest

## Data Cleaning and Normaliry transformation:

Before cleaning:

```{r}
attacks = read.csv("attacks.csv")
head(as_tibble(attacks))
```
 
After some data cleaning:
```{r}
attacks = as_tibble(attacks) %>%
  select(event_id,wounded_low,wounded_high,killed_low,killed_high) %>%
  filter(wounded_low >= 0) %>%
  filter(wounded_high >= 0) %>%
  filter(killed_low >= 0) %>%
  filter(killed_high >= 0) %>%
  mutate(wounded_average = ceiling(((wounded_low + wounded_high)/2) )) %>%
  mutate(killed_average = ceiling(((killed_low + killed_high)/2) )) %>% 
  mutate(casualties = wounded_average + killed_average) %>%
  filter(casualties < 500) %>%
  select(event_id,wounded_average,killed_average,casualties)
 head(attacks)
```

## Normality visualtization:

```{r}
par(mfrow = c(1,3))
hist(attacks$wounded_average, breaks = length(attacks$wounded_average))
hist(attacks$killed_average, breaks = length(attacks$killed_average))
hist(attacks$casualties, breaks = length(attacks$casualties))

```

The data has Poisson distribution, we have a massive positive right skew 

```{r}
par(mfrow = c(1,3))
qqPlot(attacks$wounded_average, id= FALSE)
qqPlot(attacks$killed_average, id= FALSE)
qqPlot(attacks$casualties, id= FALSE)
```



## Square root data transformation:

```{r}
par(mfrow = c(1,3))
hist(sqrt(attacks$wounded_average + 1 ))
hist(sqrt(attacks$killed_average + 1 ))
hist(sqrt(attacks$casualties + 1))

```

## Log(10) data transformation: 

```{r}
par(mfrow = c(1,3))
hist(log10(attacks$wounded_average + 1 ))
hist(log10(attacks$killed_average + 1 ))
hist(log10(attacks$casualties + 1 ))

```

## Inverse data transformation:

```{r}
par(mfrow = c(1,3))
hist(1/(attacks$wounded_average + 1 ))
hist(1/(attacks$killed_average + 1 ))
hist(1/(attacks$casualties + 1))

```

## log 10 looks like normal distribution, but what’s the problem?

```{r}
agostino.test(log10(attacks$casualties+1))
```

## too many repetitions! 

```{r}
qqPlot(log10(attacks$casualties+1),id= FALSE)
```


```{r}
attacks2 = attacks %>%
  count(casualties, sort = TRUE) %>%
  filter(casualties < 30)


      ggplot(data = attacks2, aes(x=casualties, y=n)) +
  geom_bar(stat="identity", width=0.5)

```

We did our best but you cant transform poisson distribution with low lambda

## Age and Suicidal Attacks correlation and regression 

```{r}
attackers = read.csv("attackers.csv") 
head( as_tibble(attackers) )
```

 
```{r}
attackers = attackers %>%
  as_tibble() %>%
  select(event_id,attacker_id,age_time_death,gender,birth_admin0_txt) %>%
  filter(age_time_death > 0) 
  head(attackers)
```

## Male correlation  
```{r}
male_attackers = attackers %>%
filter(gender == "Male") %>%
inner_join(attacks, by =  "event_id") %>%
select(age_time_death,wounded_average,killed_average,casualties,gender)
head(male_attackers)

```

```{r}
res<-cor.test(male_attackers$age_time_death,male_attackers$wounded_average, method="kendall")
res$p.value
```

```{r}
res2<-cor.test(male_attackers$age_time_death,male_attackers$killed_average, method="kendall")
res2$p.value
```

```{r}
res3<-cor.test(male_attackers$age_time_death,male_attackers$casualties, method="kendall")
res3$p.value
```


## Male regression  

```{r}
res4= glm(casualties ~  age_time_death, data = male_attackers , family = "poisson"	)
summary(res4)
```

## Female correlation 

```{r}
female_attackers = attackers %>%
filter(gender == "Female") %>%
inner_join(attacks, by =  "event_id") %>%
select(age_time_death,wounded_average,killed_average,casualties,gender)
head(female_attackers)
```

```{r}
fes<-cor.test(female_attackers$age_time_death,female_attackers$wounded_average, method="kendall")
fes$p.value
```

```{r}
fes2<-cor.test(female_attackers$age_time_death,female_attackers$killed_average, method="kendall")
fes2$p.value
```

```{r}
fes3<-cor.test(female_attackers$age_time_death,female_attackers$casualties, method="kendall")
fes3$p.value
```

## Female regression 

```{r}
fes4= glm(killed_average ~  age_time_death, data = female_attackers , family = "poisson"	)
summary(fes4)
```

## Male vs Female - wounded average

```{r, message=FALSE}
both_gender1 = bind_rows(male_attackers,female_attackers) %>%
  select(gender,wounded_average )
test <- wilcox.test(both_gender1$wounded_average ~ both_gender1$gender)
test$p.value
```

```{r}
ggplot(both_gender1, aes(x= wounded_average, color=gender)) +
  geom_histogram(fill="white")
```

## Male vs Female - killed average
```{r, message=FALSE}
both_gender2 = bind_rows(male_attackers,female_attackers) %>%
  select(gender,killed_average )
test2 <- wilcox.test(both_gender2$killed_average ~ both_gender2$gender)
test2$p.value
```

```{r, message=FALSE}
ggplot(both_gender2, aes(x= killed_average, color=gender)) +
  geom_histogram(fill="white")
```

## Male vs Female - Casualties


```{r}
both_gender3 = bind_rows(male_attackers,female_attackers) %>%
  select(gender,casualties )
test3 <- wilcox.test(both_gender3$casualties ~ both_gender3$gender)
test3$p.value

```

```{r, message=FALSE}
ggplot(both_gender3, aes(x= casualties, color=gender)) +
  geom_histogram(fill="white")
```

